---
title: "Regime Initialization Matrices"
author: "Josiah Leinbach"
date: "2024-07-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Seed list
set.seed(1215)
set.seed(1066)
set.seed(43)
set.seed(1415)
set.seed(597)
set.seed(1662)
set.seed(1660)
set.seed(1348)
set.seed(1611)
set.seed(1534)
set.seed(1588) -- Defeat of the Spanish Armada
set.seed(1704) -- Capture of Gilbraltar
set.seed(1805) -- Battle of Trafalgar
set.seed(1697) -- Rebuilt St. Paul's cathedral opened 
set.seed(2022) -- Queen Elizabeth II dies
set.seed(1741) -- Handel's 'Messiah' first performed
set.seed(1945) -- End of WWII
set.seed(1707) -- Act of Union (Scotland)
set.seed(1801) -- Act of Union (Ireland)
set.seed(1556) -- Archbishop Thomas Cranmer martyred
set.seed(731) -- The Venerable Bede writes "Ecclesiastical History of the English People"
set.seed(1605)
set.seed(1815)
set.seed(1170) -- Acrhbishop Thomas Becket murdered
set.seed(1688) -- Glorious Revolution

# Results
## R1 = 1, R2 = 1
```{r}
seeds <- factor(c(1215,1066,43,1415,587,1662,1660,1348,1611,1534,1588,
                  1704,1805,1697,2022,1741,1945,1707,1801,1556,
                  731,1605,1815,1170,1688))

rds_files <- list.files(pattern="\\EMR")
rds_list <- list()

for (i in 1:length(rds_files)) {
  rds_list[[i]] <- readRDS(rds_files[i])
}

df_bic <- numeric(0)

for (i in 1:25) {
  df_obj <- rds_list[[i]]
  df_bic[i] <- df_obj$BIC
}

df_1.1 <- data.frame(Seed = seeds, BIC = df_bic)
df_1.1[order(df_1.1$BIC, decreasing = F),]
```

## R1 = 2, R1 = 1
```{r}
rds_files <- list.files(pattern="\\EMR") # New directory
rds_list <- list()

for (i in 1:length(rds_files)) {
  rds_list[[i]] <- readRDS(rds_files[i])
}

df_bic <- numeric(0)

for (i in 1:25) {
  df_obj <- rds_list[[i]]
  df_bic[i] <- df_obj$BIC
}

df_2.1 <- data.frame(Seed = seeds, BIC = df_bic)
df_2.1[order(df_2.1$BIC, decreasing = F),]
```

